CRUSE to Safe Cycling in Ireland

### 2023-10-03 paper.qmd
Update with route network type figures
Add stats

@@

>>>>

These map are available on the 'Route types' page for each county (see [cruse.bike/limerick/route-types](https://cruse.bike/limerick/route-types)).
In addition to showing the estimated routes under each scenario, the page also presents summary statistics on the network:

- On the fastest network, 25% of the distance cycled occurs in non-hostile segments and 6% in cycle-friendly segments.

- Under the baseline scenario, 55% of the distance cycled on the quietest network occurs in non-hostile segments and 13% in cycle-friendly segments.

These statistics can be revealing: in Limerick it suggests that around half of all cycling activity occurs on network segments that are hostile (with a high inferred level of traffic stress), even when efforts are taken to avoid busy segments.
For the Fastest network, which may be more realistic for utility cycling, the proportion of cycling on hostile segments is even higher at 75%.

TODO: Add description of route types in Limerick based on local knowledge and @fig-route-types.

<!-- Add figure with a single row and subcaptions for Fastest and Quietest route types: -->

::: {#fig-route-types layout-nrow="2"}

@@

Illustration of the Fastest and Quietest route networks for central and East Limmerick.

:::
